Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-23 main.tex
minor fixes

Let $\gC$ be a linked fograph. The set of links can be seen as a unification problem
by identifying dual predicate symbols. A \bfit{dualizer} of $\gC$ is a substitution $\delta$
unifying all the links of~$\gC$. Since a first-order unification problem is either
unsolvable or has a most general unifier, we can define the notion of \bfit{most
general dualizer}. A \bfit{dependency} is a pair $\set{\single x, \single y}$ of an
existential binder $\single x$ and a universal binder $\single y$ such that the most
general dualizer assigns to $x$ a term containing $y$. A \bfit{leap} is either a
link or a dependency. The \bfit{leap graph} $\lgC$ of $\gC$ is the undirected
graph $\tuple{\vC, \lpC}$ where $\lpC$ is the set of leaps of $\gC$. A vetex set $W \subseteq \vC$ induces a \bfit{matching} in
$\gC$ if for all $w \in W$, $N(w) \cap W$ is a singleton. We say that $W$ induces a
\bfit{bimatching} in $\gC$ if it induces a matching in $\gC$ and a matching in $\lgC$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Contraction and Weakining}

@@

Knowing that $\cD$ can be permuted down over all the rules of $\FOMLL$, we
eventually obtain a derivation:
\begin{equation*}
\vlderivation{
  \vlde{\set{\weakr, \wrD,\cD,\fequ}}{\Deri'_2}{\sqns{\Gamma}}{
    \vltrl{}{\FOMLL}{\Deri'_1}{\sqns{\Gamma_0}}{
      \vlhy{\quad}}{
      \vlhy{}}{
      \vlhy{}}}}
\end{equation*}
Note that $\fequ$ is required here since the permutaion of formulas is implicit
in $\FOMLL$.

@@

There is a more direct path from a $\FOMLL$ proof $\Pi$ of a rectified
sequent $\Gamma$ to the linked fograph $\fographof\Pi$: simply take
the fograph $\graphof\Gamma$, and let the equivalence classes of
$\linkingof\Pi$ be all the atom pairs that meet in an instance of
$\ax$, and $\dsubstof\Pi$ is simply the collection of all subtitutions
of all the instances of the $\exists$-rule in $\Pi$.
%
We have chosen the more cumbersome path above because it gives us a
direct proof of Theorem~\ref{thm:MLL1->fonet}.
%
However, for translating $\FOMLS$ derivation into fonets, we employ
exactly that direct path.

@@

Hence, for a non-rectified  $\FOMLS$ derivation $\Deri$ in $\FOMLS$ we can
define its \bfit{rectification} $\rectif\Deri$ inductively, by recifying each
line, proceeding step-wise
from conclusion to premise.\footnote{As for formulas,
the rectification of a derivation is unique up to renaming of bound
variables.}

A rectified derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ determines a
substitution which maps the existential bound variables occurring in
$A$ to the terms substituted for them in the instances of the
$\exists$-rule in $\Phi$. We denote this substitution with
$\dsubstof\Phi$ and call it the \bfit{dualizer} of
$\Deri$. Furthermore, every atom occuring in the conclusion $A$ must
be consumed by a unique instance of the rule $\aiD$ in $\Deri$. This
allows us to define a (partial) equivalence relation $\linkingof\Deri$
on the atom occurrences in $A$ by $a\linkingof\Deri b$ if $a$ and $b$
are consumed by the same instance of $\aiD$ in~$\Deri$. We call
$\linkingof\Deri$ the \bfit{linking} of~$\Deri$, and define
$\fographof\Deri=\tuple{\graphof{A},\linkingof{\Deri}}$.

@@

\begin{thm}\label{thm:MLS1->fonet}
  Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be a recified derivation. Then
  $\fographof\Deri$ is a fonet and $\dsubstof{\Deri}$ a dualizer for it.
\end{thm}

@@

\begin{remark}
  There is an alternative path of proving Theorem~\ref{thm:MLS1->fonet}
  by translating $\Deri$ to an $\FOMLL$-proof $\Pi$, observing that
  this process preserves the linking and the dualizer. However, for
  this, we have to extent the construction above to the $\cut$-rule,
  and then show that linking and dualizer of a sequent proof $\Pi$ are
  invariant under cut elimation. This can be done similarly to
  unification nets in~\cite{hughes:unifn}.
\end{remark}

@@

Now we are going to show how from a given fonet
$\tuple{\gC,\linkingof\gC}$ we can construct a sequent proof $\Pi$ in
$\FOMLL$ such that $\fographof\Pi=\tuple{\gC,\linkingof\gC}$. In the
proof net literature, this operation is also called
\emph{sequentialization}. The basic idea behind our sequentialization
is to construct a proposional linked cograph, called the \bfit{frame}~\cite{hughes:unifn}
of $\gC$, in which the dependencies between the binders in $\gC$ are
encoded as links. Then we can apply the \emph{splitting tensor
theorem} to the frame, and then reconstruct the sequent proof $\Pi$.

@@

\begin{lemma}\label{lem:frame}
  A linked fograph $\gC$ induces a bimatching iff its frame $\frameof\gC$ induces a bimatching.
\end{lemma}

@@

This is the well-know splitting-tensor-theorem
\cite{girard:87,danos:regnier:89}, adapted for the presence of
$\mix$. In the setting of linked cographs, it has first been proved by
Retor\'e~\cite{retore:03,retore:??}\lutz{that ``handsome'' report he mentioned in
  the talk}. We use it now for our sequentialization:

@@

\begin{proof}
  Let $\dsubstof\gC$ be the dualizer of $\tuple{\gC,\linkingof\gC}$.  We
  proceed by induction on the size of $\Gamma$ (i.e., the number of
  symbols in it, without counting the commas). If $\Gamma$ contains a
  formula with $\vlor$-root, or a formula $\forall x.A$, we can
  immediately apply the $\vlor$-rule or the $\forall$-rule of $\FOMLL$
  and proceed by induction hypothesis. If $\Gamma$ contains a formula
  $\exists x.A$ such that the correponding binder $\single x$ in $\gC$
  has no dependency, then we can apply the $\exists$-rule, chosing the
  term $t$ as determined by $\dsubstof\gC$, and proceed by induction
  hypothesis.  Hence, we can now assume that $\Gamma$ contains only
  atoms, $\vlan$-formulas, or formulas of shape $\exists x.A$, where
  the vertex $\single x$ has dependencies. Then the frame
  $\tuple{\graphof{\frameof\Gamma},\linkingof{\frameof\Gamma}}$ does
  not induce a bimatching and contains only atoms and
  $\vlan$-formulas, and is therefore splittable. If it is mixed, then
  we can apply the $\mix$-rule to $\Gamma$ and apply the induction
  hypothesis to the two components. If it is not mixed then there must
  be a splitting tensor. If the splitting $\vlan$ is already in
  $\Gamma$, then we can apply the $\vlan$-rule and proceed by
  induction hypothesis on the two branches. However, if
  $\frameof\Gamma$ is not mixed and all splitting tensors are
  $\vlan$-formulas introduced in step~1 of the frame construction,
  then we get a contradiction as in that case there must be a $\vlor$- or $\forall$-formula in $\Gamma$.
  \lutz{can anyone give a good argument here?}
\end{proof}

@@

\begin{remark}
  Note that it is also possible to do a direct ``sequentialization''
  into the deep inference system $\FOMLS$, using the techniques
  presented in \cite{dissvonlutz} and \cite{str:MLL2}.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Unification Nets}

@@

\iffalse
We proceed by induction on the
number of connectives in $\Gamma$. In the base case, $\Gamma$ is of the form
\begin{align*}
p_1(t_{11}, \ldots, t_{1n_1}), \dual{p_1}(t_{11}, \ldots, t_{1n_1}), \ldots, \\
p_k(t_{k1}, \ldots, t_{kn_k}), \dual{p_k}(t_{k1}, \ldots, t_{kn_k}),
\underbrace{\ttt, \ldots, \ttt}_\text{$m$ times}
\end{align*} and
$\lambda$ is the linking $\set{(a_1, \cneg{a_1}), \ldots, (a_k, \cneg{a_k})}$,
where $a_i = p_i(t_{i1}, \ldots, t_{in_i})$, which equals to $\sqntl\Pi$, where
$\Pi$ is the proof consisting of $m$ instances of the $\ttt$ rule, $n$ instances
$\vlinf{\ax}{}{\sqn a_i, \cneg{a_i}}{}$ of the $\ax$ rule, and followed by
$m+k-1$ instances of the $\mix$ rule.

Now we consider the inductive cases:
\begin{itemize}
  \item $\Gamma = \Delta, A \vlor B$:
    Let $\Gamma' = \Delta, A, B$. Define $\lambda'$ on $\Gamma'$ using the same
    links as $\lambda$ by identifying the leaves of $\formtree{\Gamma'}$ with those
    of $\formtree{\Gamma}$. We now check that $\lambda'$ is a unification net:
    \begin{itemize}
      \item The most general dualizer of $\lambda$ is also the most general
dualizer of $\lambda'$ as they correspond to the same unification problem.
Hence, the unification structure $\unifstr{\lambda'}$ is equal to the
restriction of $\unifstr{\lambda}$ to the nodes of $\formtree{\Gamma'}$.
      \item Every switching graph of $\lambda'$ is acyclic: if there were some
switching graph of $\unifstr{\lambda'}$ containing a cycle, it would induce a switching
graph of $\unifstr{\lambda}$ containing also a cycle, by adding an edge from the root of
$\formtree{A}$ to the $\vlor$ node in question.
    \end{itemize}
  \item $\Gamma = \Delta, \forall x.A$:
    Let $\Gamma' = \Delta, A$. Define $\lambda'$ on $\Gamma'$ using the same
links as $\lambda$. We now check that $\lambda'$ is a unification net:
  \begin{itemize}
    \item The most general dualizer of $\lambda$ is also the most general
dualizer of $\lambda'$ as they correspond to the same unification problem.
    \item Every switching graph of $\unifstr{\lambda'}$ is acyclic: if there
were some switching graph of $\unifstr{\lambda'}$ containing a cycle, it would
induce a switching graph of $\unifstr{\lambda}$ contaiting also a cycle, by
adding an edge from the root of $\formtree{A}$ to the $\forall$ node in
question.
  \end{itemize}
  \item $\formtree{\Gamma}$ has a root $\exists x$ with no outgoing dependency
edge:
\end{itemize}
\fi
\end{proof}

@@

\todo{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

  For showing that it is also a skew fibration, we construct for
  $\Deri$ its propositional encoding $\PE\Deri$ by
  translating every line into its propositional encoding.
  \juihsuan{maybe mention that an instance of one of the other rules can be translated
into an instance of the same rule. It's trivial but may be worth mentioning.}\lutz{done below}
  The instances
  of the rules $\rectif\mfaD$ and $\rectif\mexD$ are replaced in two
  steps by:
  \begin{equation*}
    \vlderivation{
      \vlin{\rectif\acD}{}{\Scons{x\vlor(\PE{(Ax)}\vlor\PE{(Bx)})}}{
        \vlin{\fequ}{}{\Scons{(y\vlor z)\vlor(\PE{(Ay)}\vlor\PE{(Bz)})}}{
          \vlhy{\Scons{(y\vlor\PE{(Ay)})\vlor (z\vlor\PE{(Bz)})}}}}}
  \end{equation*}
  and
  \begin{equation*}
    \vlderivation{
      \vlin{\rectif\acD}{}{\Scons{x\vlan(\PE{(Ax)}\vlor\PE{(Bx)})}}{
        \vlin{\me}{}{\Scons{(y\vlor z)\vlan(\PE{(Ay)}\vlor\PE{(Bz)})}}{
          \vlhy{\Scons{(y\vlan\PE{(Ay)})\vlor (z\vlan\PE{(Bz)})}}}}}
  \end{equation*}
  respectively, where $\rectif\acD$ is a $\acD$ that renames the
  variabes---the propositional variable, as well as the first-order
  variable of the same name---as everything is recified, there is no
  ambiguity here. Any instance of a rule $\wD$, $\acD$, $\me$, or
  $\fequ$ is translated to an instance of the same rule, and
  $\rectif\cfaD$ is translated to $\rectif\acD$.

@@

  labels. Note that $\gA_1$ is not neccesarily a fograph, as binders

@@

  the premise. More precisely, we consider the following inferene rule

>>>>

Let $\gC$ be a linked fograph. The set of links can be seen as a unification problem
by identifying dual predicate symbols. A \bfit{dualizer} of $\gC$ is a substitution $\delta$
unifying all the links of~$\gC$. Since a first-order unification problem is either
unsolvable or has a most general unifier, we can define the notion of \bfit{most
general dualizer}. A \bfit{dependency} is a pair $\set{\single x, \single y}$ of an
existential binder $\single x$ and a universal binder $\single y$ such that the most
general dualizer assigns to $x$ a term containing $y$. A \bfit{leap} is either a
link or a dependency. The \bfit{leap graph} $\lgC$ of $\gC$ is the undirected
graph $\tuple{\vC, \lpC}$ where $\lpC$ is the set of leaps of $\gC$. A vertex set $W \subseteq \vC$ induces a \bfit{matching} in
$\gC$ if for all $w \in W$, $N(w) \cap W$ is a singleton. We say that $W$ induces a
\bfit{bimatching} in $\gC$ if it induces a matching in $\gC$ and a matching in $\lgC$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Contraction and Weakening}

@@

Knowing that $\cD$ can be permuted down over all the rules of $\FOMLL$, we
eventually obtain a derivation:
\begin{equation*}
\vlderivation{
  \vlde{\set{\weakr, \wrD,\cD,\fequ}}{\Deri'_2}{\sqns{\Gamma}}{
    \vltrl{}{\FOMLL}{\Deri'_1}{\sqns{\Gamma_0}}{
      \vlhy{\quad}}{
      \vlhy{}}{
      \vlhy{}}}}
\end{equation*}
Note that $\fequ$ is required here since the permutation of formulas is implicit
in $\FOMLL$.

@@

There is a more direct path from a $\FOMLL$ proof $\Pi$ of a rectified
sequent $\Gamma$ to the linked fograph $\fographof\Pi$: simply take
the fograph $\graphof\Gamma$, and let the equivalence classes of
$\linkingof\Pi$ be all the atom pairs that meet in an instance of
$\ax$, and $\dsubstof\Pi$ is simply the collection of all substitutions
of all the instances of the $\exists$-rule in $\Pi$.
%
We have chosen the more cumbersome path above because it gives us a
direct proof of Theorem~\ref{thm:MLL1->fonet}.
%
However, for translating $\FOMLS$ derivation into fonets, we employ
exactly that direct path.

@@

Hence, for a non-rectified  $\FOMLS$ derivation $\Deri$ in $\FOMLS$ we can
define its \bfit{rectification} $\rectif\Deri$ inductively, by rectifying each
line, proceeding step-wise
from conclusion to premise.\footnote{As for formulas,
the rectification of a derivation is unique up to renaming of bound
variables.}

A rectified derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ determines a
substitution which maps the existential bound variables occurring in
$A$ to the terms substituted for them in the instances of the
$\exists$-rule in $\Phi$. We denote this substitution with
$\dsubstof\Phi$ and call it the \bfit{dualizer} of
$\Deri$. Furthermore, every atom occurring in the conclusion $A$ must
be consumed by a unique instance of the rule $\aiD$ in $\Deri$. This
allows us to define a (partial) equivalence relation $\linkingof\Deri$
on the atom occurrences in $A$ by $a\linkingof\Deri b$ if $a$ and $b$
are consumed by the same instance of $\aiD$ in~$\Deri$. We call
$\linkingof\Deri$ the \bfit{linking} of~$\Deri$, and define
$\fographof\Deri=\tuple{\graphof{A},\linkingof{\Deri}}$.

@@

\begin{thm}\label{thm:MLS1->fonet}
  Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be a rectified derivation. Then
  $\fographof\Deri$ is a fonet and $\dsubstof{\Deri}$ a dualizer for it.
\end{thm}

@@

\begin{remark}
  There is an alternative path of proving Theorem~\ref{thm:MLS1->fonet}
  by translating $\Deri$ to an $\FOMLL$-proof $\Pi$, observing that
  this process preserves the linking and the dualizer. However, for
  this, we have to extent the construction above to the $\cut$-rule,
  and then show that linking and dualizer of a sequent proof $\Pi$ are
  invariant under cut elimination. This can be done similarly to
  unification nets in~\cite{hughes:unifn}.
\end{remark}

@@

Now we are going to show how from a given fonet
$\tuple{\gC,\linkingof\gC}$ we can construct a sequent proof $\Pi$ in
$\FOMLL$ such that $\fographof\Pi=\tuple{\gC,\linkingof\gC}$. In the
proof net literature, this operation is also called
\emph{sequentialization}. The basic idea behind our sequentialization
is to construct a propositional linked cograph, called the \bfit{frame}~\cite{hughes:unifn}
of $\gC$, in which the dependencies between the binders in $\gC$ are
encoded as links. Then we can apply the \emph{splitting tensor
theorem} to the frame, and then reconstruct the sequent proof $\Pi$.

@@

\begin{lemma}\label{lem:frame}
  A linked fograph $\gC$ induces a bimatching iff its frame $\frameof\gC$ induces a bimatching.
\juihsuan{induces a bimatching $\rightarrow$ has an induced bimatching}
\end{lemma}

@@

This is the well-know splitting-tensor-theorem
\cite{girard:87,danos:regnier:89}, adapted for the presence of
$\mix$. In the setting of linked cographs, it has first been proved by
Retor\'e~\cite{retore:03,retore:99}\lutz{that ``handsome'' report he mentioned in
  the talk}\juihsuan{added. Check if it's the good one.}. We use it now for our sequentialization:

@@

\begin{proof}
  Let $\dsubstof\gC$ be the dualizer of $\tuple{\gC,\linkingof\gC}$.  We
  proceed by induction on the size of $\Gamma$ (i.e., the number of
  symbols in it, without counting the commas). If $\Gamma$ contains a
  formula with $\vlor$-root, or a formula $\forall x.A$, we can
  immediately apply the $\vlor$-rule or the $\forall$-rule of $\FOMLL$
  and proceed by induction hypothesis. If $\Gamma$ contains a formula
  $\exists x.A$ such that the corresponding binder $\single x$ in $\gC$
  has no dependency, then we can apply the $\exists$-rule, choosing the
  term $t$ as determined by $\dsubstof\gC$, and proceed by induction
  hypothesis.  Hence, we can now assume that $\Gamma$ contains only
  atoms, $\vlan$-formulas, or formulas of shape $\exists x.A$, where
  the vertex $\single x$ has dependencies. Then the frame
  $\tuple{\graphof{\frameof\Gamma},\linkingof{\frameof\Gamma}}$ does
  not induce a bimatching and contains only atoms and
  $\vlan$-formulas, and is therefore splittable. If it is mixed, then
  we can apply the $\mix$-rule to $\Gamma$ and apply the induction
  hypothesis to the two components. If it is not mixed then there must
  be a splitting tensor. If the splitting $\vlan$ is already in
  $\Gamma$, then we can apply the $\vlan$-rule and proceed by
  induction hypothesis on the two branches. However, if
  $\frameof\Gamma$ is not mixed and all splitting tensors are
  $\vlan$-formulas introduced in step~1 of the frame construction,
  then we get a contradiction as in that case there must be a $\vlor$- or $\forall$-formula in $\Gamma$.
  \lutz{can anyone give a good argument here?}
\end{proof}

@@

\begin{remark}
  Note that it is also possible to do a direct ``sequentialization''
  into the deep inference system $\FOMLS$, using the techniques
  presented in \cite{dissvonlutz} and \cite{str:MLL2}.
\juihsuan{missing reference added, check if it's the right one.}
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse

\subsection{Unification Nets}

@@

We proceed by induction on the
number of connectives in $\Gamma$. In the base case, $\Gamma$ is of the form
\begin{align*}
p_1(t_{11}, \ldots, t_{1n_1}), \dual{p_1}(t_{11}, \ldots, t_{1n_1}), \ldots, \\
p_k(t_{k1}, \ldots, t_{kn_k}), \dual{p_k}(t_{k1}, \ldots, t_{kn_k}),
\underbrace{\ttt, \ldots, \ttt}_\text{$m$ times}
\end{align*} and
$\lambda$ is the linking $\set{(a_1, \cneg{a_1}), \ldots, (a_k, \cneg{a_k})}$,
where $a_i = p_i(t_{i1}, \ldots, t_{in_i})$, which equals to $\sqntl\Pi$, where
$\Pi$ is the proof consisting of $m$ instances of the $\ttt$ rule, $n$ instances
$\vlinf{\ax}{}{\sqn a_i, \cneg{a_i}}{}$ of the $\ax$ rule, and followed by
$m+k-1$ instances of the $\mix$ rule.

Now we consider the inductive cases:
\begin{itemize}
  \item $\Gamma = \Delta, A \vlor B$:
    Let $\Gamma' = \Delta, A, B$. Define $\lambda'$ on $\Gamma'$ using the same
    links as $\lambda$ by identifying the leaves of $\formtree{\Gamma'}$ with those
    of $\formtree{\Gamma}$. We now check that $\lambda'$ is a unification net:
    \begin{itemize}
      \item The most general dualizer of $\lambda$ is also the most general
dualizer of $\lambda'$ as they correspond to the same unification problem.
Hence, the unification structure $\unifstr{\lambda'}$ is equal to the
restriction of $\unifstr{\lambda}$ to the nodes of $\formtree{\Gamma'}$.
      \item Every switching graph of $\lambda'$ is acyclic: if there were some
switching graph of $\unifstr{\lambda'}$ containing a cycle, it would induce a switching
graph of $\unifstr{\lambda}$ containing also a cycle, by adding an edge from the root of
$\formtree{A}$ to the $\vlor$ node in question.
    \end{itemize}
  \item $\Gamma = \Delta, \forall x.A$:
    Let $\Gamma' = \Delta, A$. Define $\lambda'$ on $\Gamma'$ using the same
links as $\lambda$. We now check that $\lambda'$ is a unification net:
  \begin{itemize}
    \item The most general dualizer of $\lambda$ is also the most general
dualizer of $\lambda'$ as they correspond to the same unification problem.
    \item Every switching graph of $\unifstr{\lambda'}$ is acyclic: if there
were some switching graph of $\unifstr{\lambda'}$ containing a cycle, it would
induce a switching graph of $\unifstr{\lambda}$ contaiting also a cycle, by
adding an edge from the root of $\formtree{A}$ to the $\forall$ node in
question.
  \end{itemize}
  \item $\formtree{\Gamma}$ has a root $\exists x$ with no outgoing dependency
edge:
\end{itemize}
\end{proof}

@@

\todo{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\fi

@@

  For showing that it is also a skew fibration, we construct for
  $\Deri$ its propositional encoding $\PE\Deri$ by
  translating every line into its propositional encoding.
  \juihsuan{maybe mention that an instance of one of the other rules can be translated
into an instance of the same rule. It's trivial but may be worth mentioning.}\lutz{done below}
  The instances
  of the rules $\rectif\mfaD$ and $\rectif\mexD$ are replaced in two
  steps by:
  \begin{equation*}
    \vlderivation{
      \vlin{\rectif\acD}{}{\Scons{x\vlor(\PE{(Ax)}\vlor\PE{(Bx)})}}{
        \vlin{\fequ}{}{\Scons{(y\vlor z)\vlor(\PE{(Ay)}\vlor\PE{(Bz)})}}{
          \vlhy{\Scons{(y\vlor\PE{(Ay)})\vlor (z\vlor\PE{(Bz)})}}}}}
  \end{equation*}
  and
  \begin{equation*}
    \vlderivation{
      \vlin{\rectif\acD}{}{\Scons{x\vlan(\PE{(Ax)}\vlor\PE{(Bx)})}}{
        \vlin{\me}{}{\Scons{(y\vlor z)\vlan(\PE{(Ay)}\vlor\PE{(Bz)})}}{
          \vlhy{\Scons{(y\vlan\PE{(Ay)})\vlor (z\vlan\PE{(Bz)})}}}}}
  \end{equation*}
  respectively, where $\rectif\acD$ is a $\acD$ that renames the
  variables---the propositional variable, as well as the first-order
  variable of the same name---as everything is recified, there is no
  ambiguity here. Any instance of a rule $\wD$, $\acD$, $\me$, or
  $\fequ$ is translated to an instance of the same rule, and
  $\rectif\cfaD$ is translated to $\rectif\acD$.

@@

  labels. Note that $\gA_1$ is not necessarily a fograph, as binders

@@

  the premise. More precisely, we consider the following inference rule
